A Sample JFE Paper\footnotetext{Financial support from \ldots}

### 2018-03-15 Paper/Paper.tex
Adjustments to Estimation Part

\subsection{Link Between Patent Citations and Theory}
Multiple assumptions are needed to relate the various features of the patent citation dataset to our theoretical model:
\begin{itemize}
	\item Every patent represents a single innovation.
	\item Abrupt patents will receive more total citations than incremental patents.
	\item An abrupt patent receives a citation from a patent within its same classification if and only if the citing patent represents an incremental innovation within the abrupt patent’s technology cluster.
	\item Internal innovations will receive more self-citations (citations from future patents by that same company) than external innovations.
\end{itemize}
Assumptions one, two, and four are made in AK2016 based on empirical evidence (albeit of varying degrees). Assumption three is very important to our estimation scheme. It states that every incremental innovation will cite the abrupt patent that started its technology cluster, and that they will always be within the same patent classification. The provides a clear link between the data and the theoretical distribution in equations 14-15. If an abrupt innovation’s technology cluster had k incremental innovations, that abrupt innovation’s patent will receive k same-class citations.

Of course, to estimate the model we also need to identify the abrupt patents. Assumption two tells us that the abrupt patents will have more total citations (same-class plus external-class citations), but it does not give us an exact cutoff. In AK2016 they estimate that the upper ten percent of the total citation distribution contains the abrupt patents, so we use this cutoff in our baseline estimation. Later we test the robustness of our estimates to changes in this value.

Using the ten-percent cutoff, we can generate the distribution of same-class citations to abrupt patents (see figure 4). This empirical distribution will be fit to our theoretical distribution from equations 14-15 to estimate the model. Two important features of the empirical distribution is the large mass of patents at zero citations and the large upper tail.

It should be noted that, even if the four assumptions listed above are completely accurate, we would expect some abrupt patents to be wrongly classified as incremental due to our ten percent cutoff. According to our theoretical model, there is a chance that an abrupt innovation’s technology cluster will be replace very early on by another abrupt innovation, meaning that it will receive very few same-class citations. While the abrupt patent could still receive out of class citations after being replaced (and in fact, we do see many patents with zero same-class citations but many external citations), it could not receive enough to be classified as abrupt. Thus, we expect the empirical distribution in figure 4 to underestimate the amount of abrupt patents with low numbers of citations. The impact of this potential bias on our estimation is discussed below.

\subsection{MLE Estimation}

According to equations 14-15, the theoretical citation distribution of abrupt patents only depends on three parameters: $\alpha$, $\lambda_{inc,0}$, and $\lambda_{abr, int} + \tau$. In addition, the distribution is identical at equal ratios of the arrival rate parameters, so it actually only depends on two independent parameters: $\alpha$ and $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$. Intuitively, $\alpha$ governs rate at which the incremental innovation step size decays after multiple incremental innovations ($\alpha$ equal to one implies a constant step size). The value of  $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$ is determined by the relative amount of incremental compared with abrupt innovations in the entire economy.

Given a set of parameter values, the resulting citation distribution looks like a gamma distribution, with a large upper tail and the possibility of a mode greater than zero. A larger value of $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$  means that there are relatively more abrupt innovations, which means that more product lines will be replaced before their originating patents can accrue a large number of citations. Thus, increasing $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$ shifts the distribution to the left. Reducing the value of $\alpha$ means that the firms will invest relatively more in incremental innovation early in the product lifecycle (due to the diminishing returns to incremental innovation). For low enough values of $\alpha$, this can lead to a peak in the distribution at a citation value greater than zero, as firms almost always invest in the first incremental innovation but invest increasingly less in the late ones. Theoretical graphs for various parameter values are shown in figure 5.

We estimate the two parameters using maximum likelihood estimation. Our theoretical model gives a probability mass distribution for every whole number of citations, but the actual data shows fractional values (this is because, to address the fact that newer patents did not have as long of a time to gain citations, we used a measure of expected citations that allowed for non-whole numbers). To address this, we rounded the expected citation variable to the nearest whole number, and then took the likelihood as the theoretical pmf value at that point.

@@

@@

>>>>

\subsection{Link Between Patent Citations and Theory}
Multiple assumptions are needed to relate the various features of the patent citation dataset to our theoretical model:
\begin{itemize}
	\item i) Every patent represents a single innovation;
	\item ii) Abrupt patents will receive more total citations than incremental patents;
	\item iii) An abrupt patent receives a citation from a patent within its same classification if and only if the citing patent represents an incremental innovation within the abrupt patent’s technology cluster;
	\item iv) Internal innovations will receive more self-citations (citations from future patents by that same company) than external innovations.
\end{itemize}
Assumptions \textit{i}, \textit{ii}, and \textbf{iv} are made in Akcigit and Kerr (2016) based on empirical evidence (albeit of varying degrees). Assumption \textit{iii} is very important to our estimation scheme and a natural one to make. It states that every incremental innovation will cite the abrupt patent that started its technology cluster, and that they will always be within the same patent classification. This provides a clear link between the data and the theoretical distribution in equations \ref{eq:eta0} and \ref{eq:etak}. If the technology cluster of an abrupt innovation had k incremental innovations, the related patent will receive k same-class citations.

Of course, in order to estimate the model we also need to identify the abrupt patents. Assumption \textit{ii} states that abrupt patents will have more total citations (same-class plus external-class citations), but it does not give us an exact cutoff. In Akcigit and Kerr (2016), they estimate that the upper 10\% of the total citation distribution contains the abrupt patents, so we use this cutoff in our baseline estimation. Later we test the robustness of our estimates to changes in this value.

Using the 10\% cutoff, we can generate the distribution of same-class citations to abrupt patents (c.f. figure \ref{fig:SameClassDistr}). This empirical distribution will be fit to our theoretical distribution from equations \ref{eq:eta0} and \ref{eq:etak} to estimate the model. Two important features of the empirical distribution are the large mass of patents at zero citations and the large upper tail.

It should be noted that, even if the four assumptions listed above are completely accurate, we would expect some abrupt patents to be wrongly classified as incremental due to our 10\% cutoff. According to our theoretical model, there is a chance that the technology cluster of an abrupt will be replaced very early on by another abrupt innovation, meaning that it will receive very few same-class citations. While the abrupt patent could still receive out of class citations after being replaced (and in fact, we do see many patents with zero same-class citations but many external citations), it could not receive enough to be classified as abrupt. Thus, we expect the empirical distribution in figure \ref{fig:SameClassDistr} to underestimate the amount of abrupt patents with low numbers of citations. The impact of this potential bias on our estimation is discussed below.

\subsection{Maximum Likelihood Estimation}

According to equations \ref{eq:eta0} and \ref{eq:etak}, the theoretical citation distribution of abrupt patents only depends on three parameters: $\alpha$, $\lambda_{inc,0}$, and $\lambda_{abr, int} + \tau$. In addition, the distribution is identical at equal ratios of the arrival rate parameters, so it actually only depends on two independent parameters: $\alpha$ and $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$. Intuitively, $\alpha$ governs rate at which the incremental innovation step size decays after multiple incremental innovations ($\alpha$ equal to one implies a constant step size). The value of $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$ is determined by the relative amount of incremental compared with abrupt innovations in the entire economy.

Given a set of parameter values, the resulting citation distribution looks like a gamma distribution, with a large upper tail and the possibility of a mode greater than zero. A larger value of $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$  means that there are relatively more abrupt innovations, which means that more product lines will be replaced before their originating patents can accrue a large number of citations. Thus, increasing $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$ shifts the distribution to the left. Reducing the value of $\alpha$ means that the firms will invest relatively more in incremental innovation early in the product life-cycle (due to the diminishing returns to incremental innovation). For low enough values of $\alpha$, this can lead to a peak in the distribution at a citation value greater than zero, as firms almost always invest in the first incremental innovation but invest increasingly less in the late ones. Theoretical graphs for various parameter values are shown in figure \ref{fig:ImpactPar}.

We estimate the two parameters using maximum likelihood estimation. Our theoretical model gives a probability mass distribution for every whole number of citations, but the actual data shows fractional values (this is due to the diffusive correction factor from Hall et al., 2001). To address this, we rounded the expected citation variable to the nearest whole number, and then took the likelihood as the theoretical PMF value at that point.

@@

\begin{table}[htbp] \centering \captionsetup{width=5.8in}
    \caption{\label{MLETable}\textit{Results from the maximum likelihood estimation}}
	\centering
	\begin{tabular}{l llp{1.5cm} p{0.5cm} llp{1.5cm} llp{1.5cm}}
	\toprule
	MLE & \multicolumn{1}{c}{$\alpha$} & \multicolumn{1}{c} {$\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$} \\ 
	\midrule
	Results & 10.06 & 7.39\\
	Mean of first 5 seq. ratios & 0.57 & 0.88\\
	Sum of first 2 bins & 0.26 & 0.22\\
	R\&D Intensity & 0.068 & 0.068\\
	Criterion & & 0.386\\
	\midrule
	$(\hat{\tau} + \hat{\lambda}_{int,abr}, \hat{\lambda}_{inc,0}, \hat{\alpha}) = (0.047, 0.351, 1)$\\
	\bottomrule
	\end{tabular}
\end{table}

@@

\begin{figure}[htb]\centering \captionsetup{width=5.8in}
    \fbox{\resizebox{3.0in}{2.0in}{\includegraphics{SameClass_hist.png}}}
    \caption{\label{fig:SameClassDistr}\textit{Distribution of same-class abrupt patents by the number of received citations.}}
\end{figure}

\begin{figure}[htb]\centering \captionsetup{width=5.8in}
    \fbox{\resizebox{3.0in}{2.0in}{\includegraphics{Impact_parameters.png}}}
    \caption{\label{fig:ImpactPar}\textit{Theoretical distribution of patents per number of citations for different sets of parameters.}}
\end{figure}
